I am very excited to be applying for the role of Data Coach at Multiverse.
As someone who has recently completed a PhD in quantitative research, I am acutely aware of the monopoly of university higher education and how it very often fails to adequately enable students to pursue their ambitions.
The mission of Multiverse, to offer viable and equal alternatives to university education, strongly resonated with me and is something I would very much like to be a part of.
My previous role coaching doctoral students in quantitative research skills was one of the most rewarding aspects of my PhD.
I hope my passions for engaging students and sharing my background in quantitative research and industry will be of great value to the Multiverse team.


Throughout my PhD, and more recently my data science internship with the NHS, I have worked extensively with modern practises in data science and software engineering.
I was also actively involved in developing and delivering teaching materials to a diverse range of doctoral student seeking to develop quantitative research skills.
In addition, I have worked 1:1 with undergraduate students completing final year projects in quantitative biology.
Importantly, I am comfortable delivering materials remotely and engaging students online, as was necessitated throughout the pandemic.
I hope that my coaching experience, in combination with my research background and data science work with the NHS, will provide a unique perspective when delivering materials to Multiverse apprentices. 

Thank you very much for considering my application to join your team and be a part of the Multiverse mission.
I feel that this role perfectly combines my passions of applying data science to solve real-world problems with my ambition to help others build their own careers in data.
I very much look forward to hearing back from you and learning more about what this role has to offer.
 